---
title: "GLM"
author: "Alok Kumar"
date: "4 February 2018"
output: 
  pdf_document:
      number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# GLM Introduction:

In statistics, the generalized linear model (GLM) is a flexible generalization of ordinary linear regression that allows for response variables that have error distribution models other than a normal distribution.

GLM have three components:
1. Distribution of Responce variable. (y ~ exponential family)
2. Linear predictor
3. Link function

# Experiment Details

The data taken show the distribution of 1607 women interviewed in fiji fertility survey of 1975, classified by current age , level of education, desire for more children, and contraceptive use.

```{r}
data = read.table(".//Data//Cont by Age.txt" , head(T))
attach(data)
Prop = Using/Total
plot(Age,Prop)
```

Converting data trom using and Total to using and not using.
We are doing this for odd ratio.
cbind - bind the two column and create matrix.
```{r}
y = cbind(Using, Total-Using)
y
```

# One factor Model
GLM in which only one factor exist.

Logistic regression model for each age group using the y(parameter estimates calculated)

```{r}
g1 = "Group 1 (age < 25)" 
g2 = "Group 2 (age 25 - 29)" 
g3 = "Group 3 (age 30 - 39)" 
g4 = "Group 4 (age 40 - 49)" 
```

```{r}
glmOddvsAgeFactor = glm(y~factor(Age) , family = binomial(link = logit))

```

Systematic component:
g(u) = log(p/1-p) = b0 + b1x1 + b2x2 + b3x3

Random component :
yi | x1,x2,x3 ~ B(n,p)
where x1 if Age = 2 (25-29)
      x2 if Age = 3 (30-39)
      x3 if Age = 4 (40-49)
      
```{r}
summary(glmOddvsAgeFactor)
```

## Odds of using contraception for each group
Calculation logit(p) = coefficient

logit(p) = log(p/1-p) = log(odd) = coefficient 

odd = exp(coefficient)

### Odd interpretation for `r g1`

```{r}
ageGroup1Odd = exp(glmOddvsAgeFactor$coefficients[1])
ageGroup1Odd
```

Therefore odd of someone using contraceptive in `r g1` is `r ageGroup1Odd*100`%. 

### Odd interpretation for `r g2`

```{r}
ageGroup2Odd = exp(glmOddvsAgeFactor$coefficients[1] + glmOddvsAgeFactor$coefficients[2])
ageGroup2Odd
```

Therefore odd of someone using contraceptive in `r g2` is `r ageGroup2Odd*100`%. 

### Odd interpretation for `r g3`

```{r}
ageGroup3Odd = exp(glmOddvsAgeFactor$coefficients[1] + glmOddvsAgeFactor$coefficients[3])
ageGroup3Odd
```

Therefore odd of someone using contraceptive in `r g3` is `r ageGroup3Odd*100`%. 

### Odd interpretation for `r g4`
 
```{r}
ageGroup4Odd = exp(glmOddvsAgeFactor$coefficients[1] + glmOddvsAgeFactor$coefficients[4])
ageGroup4Odd
```

Therefore odd of someone using contraceptive in `r g4` is `r ageGroup4Odd*100`%. 

## Inter group comparison

### `r g2` in compare of `r g1`

```{r}
oddg2vsg1 = ageGroup2Odd/ageGroup1Odd
oddg2vsg1Per = (oddg2vsg1 - 1)*100 


```
```{r echo=FALSE}
moreOrLess = function(value){
  if(value > 0){
  return("more")
  }else{
  return("less")
  }
} 

```



`r g2` is `r oddg2vsg1Per` % `r moreOrLess(oddg2vsg1Per)` likely to use contraceptive then `r g1`


### `r g3` in compare of `r g2`

```{r}
oddg3vsg2 = ageGroup3Odd/ageGroup2Odd
oddg3vsg2Per = (oddg3vsg2 - 1)*100 


```

`r g3` is `r oddg3vsg2Per` % `r moreOrLess(oddg3vsg2Per)` likely to use contraceptive then `r g2` 















      
      
      
      
      
      
      
      
      
      
      
      




